Adopting agile software development in the large organizations: A systematic literature review

### 2014-06-24 journal/article.tex
Clarifications

The definition of large scale was discussed in a workshop at XP2013
\cite{Dingsoyr2013a}. Proceeding the workshop, Dingsøyr et al.
compiled a description of the definition of large scale \cite{Dingsoyr2013b}.
The most common view in the XP2013 workshop was that the involvement of many
people is the main factor in large scale \cite{Dingsoyr2013b}.

@@

Based on these findings we defined large scale in the scope of this research to
denote organizations with 50 or more people. These 50 people would not all need
to be developers, but they should be part of the development organization. For
instance, Scrum masters and software architects would be counted in. As some
studies presented the number of teams rather than number of people, we
correspondingly defined large scale to denote development efforts involving at
least 6 teams. Having 6 teams with an average teams size of 6 people, plus a
number of supporting staff, can reasonably be considered to form an organization
of 50 people.

>>>>

The definition of large scale was recently discussed in a workshop at XP2013
\cite{Dingsoyr2013a}. Proceeding the workshop, Dingsøyr et al.
compiled a description of the definition of large scale \cite{Dingsoyr2013b}.
The most common view in the XP2013 workshop was that the involvement of many
people is the main factor in large scale \cite{Dingsoyr2013b}.

@@

Based on these findings we defined large scale in the scope of this research to
denote organizations with 50 or more people. These 50 people would not all need
to be developers, but they should be part of a single software development
organization. For instance, Scrum masters and software architects would be
counted in. As some studies presented the number of teams rather than number of
people, we correspondingly defined large scale to denote development efforts
involving at least 6 teams. Having 6 teams with an average teams size of 6
people, plus a number of supporting staff, can reasonably be considered to form
an organization of 50 people.
